% This file contains definitions of various fields used
% in various places throughout the thesis (in the title
% pages mostly). Whatever isn't define here has some
% default (and usually irrelevant) text.

\authorEnglish{Doron Behar}
\authorHebrew{דורון בכר}

%\titleEnglish{Improved methods \\ for the cultivation of lettuce \\ on the coastal plane}
%\titleHebrew{שיטות משופרות \\ לגידול חסה במישור החוף}

\disciplineEnglish{Physics}
\disciplineHebrew{פיזיקה}

\supervisionEnglish{This research was carried out under the supervision of Prof. Yuval Shagam and Yotam Soreq, in the Faculties of Chemistry and Physics, respectively.}
\supervisionHebrew{המחקר בוצע בהנחייתם של פרופסור יובל שגם ופרופסור יותם שורק מהפקולטה לכימיה והפקולטה לפיזיקה, בהתאמה.}

\GregorianDateEnglish{January 2012}
\GregorianDateHebrew{ינואר \textenglish{2012}}
\JewishDateEnglish{Tevet 5772}
\JewishDateHebrew{טבת התשע"ב}

%\financialAcknowledgementEnglish{The Technion's funding of this research is hereby acknowledged.}
%\financialAcknowledgementHebrew{הכרת תודה מסורה לטכניון על מימון מחקר זה.}

\publicationInfoEnglish{%
Some results in this thesis have been published as articles by the author and research collaborators in conferences and journals during the course of the author's doctoral research period, the most up-to-date versions of which being:

\butcheredbibliography{front/pubinfo.bib}
}
\ethicsStatementEnglish{%
The research underlying this thesis was conducted honestly, in accordance with the ethical standards customary in academia. This applies, in particular, to the collection, processing and presentation of data, the description of and comparison with previous research work, etc. 
Also, the report on research activities and findings in this work is thorough and honest in accordance with the aforementioned standards.

}

\publicationInfoHebrew{%
חלק מן התוצאות בחיבור זה פורסמו כמאמרים מאת המחבר ושותפיו למחקר בכנסים ובכתבי-עת במהלך תקופת מחקר הדוקטורט של המחבר, אשר גרסאותיהם העדכניות ביותר הינן:%

\begin{otherlanguage}{english}%
\butcheredbibliography{front/pubinfo.bib}
\end{otherlanguage}%
}

\ethicsStatementHebrew{%
המחקר שבבסיס חיבור זה נערך כולו ביושר, ולפי אמות המידה האתיות המקובלות באקדמיה. בפרט אמורים הדברים בפעילויות איסוף הנתונים, עיבודם והצגתם, התייחסות והשוואה למחקרים קודמים וכו', ככל שהיוו חלק מן המחקר. כמו כן, הדיווח על המחקר ותוצאותיו בחיבור זה הוא מלא וישר, לפי אותן אמות מידה.

}
\addbibresource{back/general.bib}
% \thesisbibstyle{trad-alpha}
